\textit{
Suppose $X,Y,Z$ are Banach spaces and 
%
\begin{align*}
  B:X\times Y \to Z
\end{align*}
%
is bilinear and continuous. Prove that there exists $M<\infty$ such that 
%
\begin{align*}
  \norm{B(x, y)}
  \leq 
  M \norm{x}\norm{x} \quad (x\in X, y\in Y).
\end{align*}
%
Is completeness needed here?}
\begin{proof}%
% % % % % % % 
% FIRST PART %
% % % % % % % 
The answer is: No. To prove this, we only assume that %
%
  $\mathit{X}$, $\mathit{Y}$, $\mathit{Z}$ %
%
are normed spaces. %
%
Since $B$ is continous at the origin, there exists a positive $r$ %
such that %
%
\begin{align}\label{bound for B}
  \norm{x} + \norm{y} < r \Rightarrow %
  \norm{B(x, y)} < 1.
\end{align}
%
%
Given nonzero $\mathit{x}, \mathit{y}$, let $s$ range over $]0, r[$so that the folllowing bound %
%
\begin{align}
  \norm{B(x, y)} = \frac{4\norm{x}\norm{y}}{s^2} %
    \left\|
      B \left(\frac{s}{2\norm{x}}x, \frac{s}{2\norm{y}}y \right)
    \right\|
  \overset{(\ref{bound for B})}{<} \frac{4 \norm{x} \norm{y}}{s^2}
  %\quad (x\neq 0, y \neq 0)
\end{align}
is effective. % 
It is now obvious that %%
%
\begin{align}
    B(x, y) \leq %
    \frac{\!\!\!4\!}{\,s^{\,2}}\norm{x}\norm{y} 
    \tendsto{s}{r}
    \frac{\!\!\!4\!}{\,r^{\,2}}\norm{x}\norm{y}
    \quad ((x, y) \in X \times Y); 
\end{align}
%
which achieves the proof.\\\\ %
% % % % % % % %
% SECOND PART %
% % % % % % % %
As a concrete example, choose %
%
  $X = Y = Z = C_c(\R)$, %
%
topologized by the supremum norm. %
%
$C_c(\R)$ is not complete %
%
(see 5.4.4 of \cite{AnalyseIII}), %
%
nevertheless the bilinear product %
%
\begin{align}
  \begin{aligned}
    B: &&& C_c(\R)^{2} & \to      &&& C_c(\R) \\\nonumber 
      &&& (f, g)       & \mapsto  &&& f \cdot g
  \end{aligned}
\end{align}
%
is bounded (since %
    $\norma{\infty}{f\cdot g} \leq \norma{\infty}{f}\cdot \norma{\infty}{g}$%
), %
and continuous. To show this, pick a positive scalar %
$\epsilon $ smaller than $1$, provided any $(f, g)$. Next, define %
%
\begin{align}
  r \triangleq \frac{\epsilon}{1 + \norma{\infty}{f} + \norma{\infty}{g}} < 1. %
\end{align}
%
We now restrict $(u, v)$ to a particular neighborhood of $(f, g)$. %
More specifically,  
\begin{align}
  \norma{\infty}{f-u} + \norma{\infty}{g-v} < r. %
\end{align}
%
Next, remark that %
%
  $\norma{\infty}{u} \leq r + \norma{\infty}{f}$ %
%
and so obtain (bear in mind that $r < 1$)%
%
  \begin{align}
    \norma{\infty}{fg - uv} 
      & =
    \norma{\infty}{(f-u) \cdot g + u \cdot (g-v)} \\
      & \leq
    \norma{\infty}{f-u} \cdot \norma{\infty}{g} + 
    \norma{\infty}{u}   \cdot \norma{\infty}{g-v} \\
      & < r \cdot \norma{\infty}{g} + (r + \norma{\infty}{f}) \cdot r \\
      & < r \cdot (r + \norma{\infty}{f} + \norma{\infty}{g})  \\
      & < \epsilon.
  \end{align}
%
Since $\epsilon$ was arbitrary, it is now established that $B$ continuous %
at every $(f, g)$.
\end{proof}
% END
